Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-04 draft.tex
some annotations in last section

>>>>

\begin{itemize}
        We introduce a bi-Lipschitz mapping 
            \Psi : |\calR'| \rightarrow |\calK|
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
        We define 
            \Psi(x) 
            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
        One easily verifies that this defines a continuous mapping $\Psi$. 
        By the same line of thought, we see that it is invertible with inverse 
            \Psi^{-1}(x) 
            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x
        We analyze its Jacobian. 
        First, by assumption,
            \Psi(x) 
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
        In what follows, $y \in \bbR^n$. We observe 
            \Jacobian \Psi(x) \cdot y 
                ( A_{{G}}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot x )
                ( A_{{G}}^{-t} \vecone \cdot x )
                ( A_{K}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot x )^2
            x
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
                ( A_{{G}}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot  x )
            x
                ( A_{{G}}^{-t} \vecone \cdot x )
                ( A_{K}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot  x )^2
            x
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
                ( A_{{G}}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot  x )
            x
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
                    ( A_{K}^{-t} \vecone \cdot y ) 
                    ( A_{K}^{-t} \vecone \cdot  x ) 
                x
        We see that the last summand is an oblique projection of $y$. 
        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes. We conclude that 
             A_{K}^{-t} \vecone \cdot x 
             \vecone \cdot A_{K}^{-1} x 
             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
        Together with the Xu-Zikatanov inequality, we obtain the upper bound 
            \matnorm{ \Jacobian \Psi(x) }
            \sqrt{n}
            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
            n
            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
        By completely analogous arguments, we find 
            \matnorm{ \Jacobian \Psi^{-1}(x) }
            \sqrt{n}
            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-1} ) }
            n
            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-2} ) }
            \Xi := \Psi \circ \Theta
        is a mapping from ${G}$ onto $U = \overline{\patch_{\calT}(S) \setminus {G}}$.
        It preserves the interface from ${G}$ onto $U$.

        \item 
        \color{red}
        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.

        A similar argument applies to the triangulation $\calR'$. 
        We conclude that $\Xi$ is bi-Lipschitz. 
        \color{black}

        \item 
        \color{red}
        We collect several geometric facts.

        \item 
        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
        Each bisection step reduces the diameter by at most a factor of one half,
        and it reduces the volume always by a factor of one half. 
        We use the estimates in Lemma~\ref{lemma:measurerelationships}.
        When $K \in \calK \cup \calS'r$, then 
        \begin{align*}
             \sigma_{\max}( A_{K}^{-1} )
             &\leq 
             \Czwei{n} \geometricshapemeasure(K) \diam(K)
             \leq 
             2 \Czwei{n} \geometricshapemeasure(\calT) \diam(K)^{-1}
             \\
             \sigma_{\min}( A_{K}^{-1} )^{-1}
             &= 
             \sigma_{\max}( A_{K} ) 
             \leq 
             \Ceins{n} \diam(K),
             \\ 
             \geometricshapemeasure( A_{K} )
             &\leq 
             \Cdrei{n} \geometricshapemeasure(K) \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
             .
        \end{align*}
        When ${G} \in \calR'$ is not our original simplex, then 
        \begin{align*}
             \sigma_{\max}( A_{{G}}^{-1} )
             &\leq 
             \Czwei{n} \geometricshapemeasure({G}) \diam({G})
             \leq 
             4 \Czwei{n} \geometricshapemeasure(\calT) \diam(G)^{-1},
             \\
             \sigma_{\min}( A_{{G}}^{-1} )^{-1}
             &= 
             \sigma_{\max}( A_{{G}} ) 
             \leq 
             \Ceins{n} \diam({G}),
             \\ 
             \geometricshapemeasure( A_{{G}} )
             &\leq 
             \Cdrei{n} \geometricshapemeasure({G}) \leq 4 \Cdrei{n} \geometricshapemeasure(\calT)
             .
        \end{align*}
        All the diameters above are comparable up to a factor of $\diameterratio(\calT)$.
        In summary,
        \begin{gather*}
            \matnorm{ \Jacobian \Theta_{|K}      } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
            ,
            \qquad 
            \matnorm{ \Jacobian \Theta_{|K}^{-1} } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
            ,
            \\
            \matnorm{ \Jacobian \Xi(x) }
            \leq 
            \sqrt{n}
            4 
            \geometricshapemeasure(\calT) 
            \Ceins{n} 
            \Czwei{n} 
            \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
            \left( 
                1
                + 
                n
                2 \Cdrei{n} \geometricshapemeasure(\calT)
                4 
                \geometricshapemeasure(\calT) 
                \Ceins{n} 
                \Czwei{n} 
                \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
            \right) 
            2 \Cdrei{n} \geometricshapemeasure(\calT)
            ,
            \\
            \matnorm{ \Jacobian \Xi^{-1}(x) }
            \leq 
            \sqrt{n}
            2 
            \geometricshapemeasure(\calT) 
            \Ceins{n} 
            \Czwei{n} 
            \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
            \left( 
                1
                + 
                n
                2 \Cdrei{n} \geometricshapemeasure(\calT)
                2 
                \geometricshapemeasure(\calT) 
                \Ceins{n} 
                \Czwei{n} 
                \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
            \right) 
            2 \Cdrei{n} \geometricshapemeasure(\calT)
            .
        \end{gather*}
\end{itemize}
